%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\cvtheme[blue]{custom}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Dhara}
\familyname{Sheth}
% optional, remove the line if not wanted
\address{1717 SW Park Ave, Apt 511 Portland Oregon}{97201} 
% optional, remove the line if not wanted
\mobile{404-913-4272}                    % optional, remove the line if not wanted
\email{dhara@sheth.net.in}                      % optional, remove the line if not wanted
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Objective}
\cventry{}{To secure a full time School Counseling position. My aim is to work with diverse student populations}{}{}{}{}

\section{Education}
\cventry{09.2011--present}{M.S}{School Counseling}{Portland State University - Oregon}{GPA 3.92}{ Anticipated graduation June 2014}
\cventry{06.2006--03.2008}{M.A}{Counseling Psychology}{Maharaja Sayajirao University} {Baroda, India}{}{}{}
\cvlistitem[]{\emph{Dissertation} To study the attitudes of students towards public display of affection.}
\cventry{06.2003--04.2006}{B.A}{Psychology}{Gujarat University - India}{}{}  % arguments 3 to 6 are optional

\section{Profile}
\cvlistitem[]{Self directed and highly motivated with an eagerness to help others in need.}
\cvlistitem[]{Empathic and attentive listener}
\cvlistitem[]{Exceptional understanding of problems faced by cultural minorities.}
\cvlistitem[]{Strong organization, prioritization and time management skills}
\cvlistitem[]{Exceptional multi tasking abilities.}

\section{Certified Courses \& Projects}
\cvlistitem[\emph{ASIST}] {- Applied Suicide Intervention Skills Training}
\cvlistitem[\emph{CGCP}] {- Model Comprehensive Guidance and Counseling Program for middle school as per ASCA guidelines}
\cvlistitem[\emph{Transition to Middle School}] {-  Program for 5th grade students and parents}
\cvlistitem[\emph{Basic Counseling Skills}] {Workshop at Tangram}
\cvlistitem[\emph{Hatha Yoga}] {at M.S University}



\section{Experience}
\cventry{2012.09--present}{Graduate Mentor for General Ed. Sophomore level classes}{University Studies, Portland State University}{
As a graduate mentor, I was tasked with conducting sessions of 12 students each for a class of 36 students.My duties included teaching, assisting students in research and writing process, group facilitation, community building, connecting students with appropriate resources and working on student retention.
% This is a scholarship position within the University Studies Department. As a peer mentor I planned lessons and led bi-weekly mentor sessions for groups of freshman level students. I also collaborated with PSU faculty and UNST staff to fulfill the university’s core requirements. My primary role was to help my students acclimate to the unique college culture of PSU. 
}{}{}
\cventry{Fall, 2012}{International Student Peer Mentor }{Portland State University}{
This position included mentoring 8 to 9 international students during their initial term. As student peer mentors, we served as bridges for the international students from their parent culture to that of Portland State University, and United States as a whole. My duties included cultural advising and peer support for any problems they face.
}{}{}
\cventry{2011.10--2012.08}{Student Teacher}{Helen Gordon Child Development Center, Portland} {
Working in infant toddler section assisting physical emotional and social needs of children, with an emphasis on Reggio Emilia approach.
}{}{}
\cventry{2011.10--2012.03}{Student Teacher}{Beverly Cleary , Portland Public School, Portland}{
As part of effective teaching and class room management in Portland State University, taught a class of 30 students in grade IV. The subjects taught included math, team building and social sciences.}{}{}
\cventry{2009.01--2011.04}{\textbf{Senior School Educator}}{Eklavya School, Ahmedabad - \httplink{www.eklavya.org}}{India}{}{
Taught Psychology in High School and History-Geography in Middle School, and was responsible for guiding students in psychology related research. I was also part of several committees such as group counseling, organizing events, seminars \& competitions, leading field visits, survey and nature camps within the school.}
\cventry{2008.05--2008.12}{Trainee Psychologist}{Tangram}{India}{
As a trainee psychologist, conducted seminars and workshops on effective study habits, time management and stress management for high school students and their parents. Conducted play therapy sessions with young children. I was also involved in several psychological testing sessions}{}
\cventry{2008.01--2008.03}{School Counselor Intern}{Bhartiya Vidya Bhavans school}{Baroda, India}{
As a school counselor intern, my duties included play therapy for elementary school children. I also organized group sessions with elementary and high school children on team building and life skills}{}
\cventry{2006.12--2007.11}{Counseling Clinic Intern}{Counseling Center, Dept. Psychology - MS University}{Baroda, India}{My duties included counseling and psychological testing for the clients. I had 4 ongoing clients and administered psychological testing for 20 others.}{}

\section{Affiliations}
\cventry{Winter, 2013}{Member} {Pi Sigma Upsilon chapter of Chi Sigma Iota [CSI]}{Portland State University}{}{}{}{}
\cventry{Winter, 2013}{Member} {American Counseling Association}{ACA}{}{}
\cventry{Spring, 2012}{Member} {Oregon School Counseling Association}{OSCA}{}{}

\section{Awards}
\cventry{Fall, 2010}{Best Educator in Senior School for 2009-2010} {Award}{Eklavya School}{}{}

%\pagebreak

\section{Community \& Volunteer Work}
\cvlistitem[\emph{Oregon Food Bank} (Volunteer)] {with Khiwanis club} 
\cvlistitem[\emph {IRCO}] {Immigrant and Refugee Community Organization - in home tutor}
\cvlistitem[\emph{World Mental Health Week}]{Creating awareness about mental health}
\cvlistitem[\emph{National Social Service - India,}]{Representative from St. Xavier's College, Gujarat, for three years}
\cvlistitem[\emph{Youth Hostel Association - India,}]{Camp leader, Ahmedabad main unit.}

\section{Languages}
\cvlistitem[]{English, Hindi, Gujarati}

%\section{Address}
%\cvlistitem[] {3854 SE Yamhill St.\\
%Portland, OR\\
%Zip: 97214}
\end{document}


%% end of file `template_en.tex'.
